\section{Battle}

\subsection{Sophie}
When Sophie uses Calcifer's abilities to fight, she usually calls his name.

All Calcifer's attacks make a burning-like noise.

\subsection{Guard}
The guards can insult and threaten Sophie:
\begin{itemize}
	\item Better for you if you surrender!
	\item Stop! You're under arrest!
	\item Bad idea, little girl.
	\item You're going to jail.
	\item You can't escape!
\end{itemize}

The guards wear boots, so their steps are quite noisy.

Their arquebus make a noisy gunshot sound.

When harmed, the guards make a grunt of pain.

When defeated, the guards moan.

\subsection{Demon}
The demon can growl and scream.

Their steps are not very noisy, but the player can hear them coming because of their cries.

When attacking, they roar and their claws make a scratch-like sound.

When harmed, the demons make a cry of pain.

When defeated, the demons emit a short cry.

\subsection{Captain}
The captain can insult and threaten Sophie:

%During the fight:
\begin{itemize}
	\item Better for you if you surrender!
	\item You can't beat me, little girl.
	\item I'll bring you to jail.
	\item I'll make the Queen proud of me!
	\item \textbf{After loosing half HP}: Don't act like you have defeated me, little girl! I won't fail the Queen!
\end{itemize}

The captain's steps make a sound similar to the one made by the guards because of this boots, but it is louder because of his size.

When he transforms in half demon, his body makes a burning-like noise. A similar, milder sound goes on until the transformation ends.

The Magic claw attack makes a loud scratch-like sound. The Fireball attack makes a loud burning-like sound.

When harmed, the captain makes a beast-like grunt of pain.

When defeated, the captain moans.
