\pagebreak % Used to keep everything on the same page.

\section{Main themes}

In the game story there are some recurrent moral themes:

\begin{itemize}
\item \textit{Choice}: the player is always asked to make choices that will influence the rest of the game. \\
  He/She can choose to overcome obstacles using a reflective approach or brute force. \\
  In the finale, the player can choose to spare the main antagonist or kill her.

\item \textit{Love}: the story of the game is created around two love stories. \\
  The first one is the love story of Sophie and Howl. Sophie exalts the love theme because she would do anything to rescue Howl. \\
  The second one is Mizar’s unrequited love that has made her the antagonist.

\item \textit{Vengeance}: vengeance is the reason why the war is going on. Mizar is animated by vengeance caused by her struggle in love.

%\item \textit{Conflict}: there is one main conflict in the story, the war between the Kingdom of Strangia and the Kingdom of Ingary. \\
%  On one side, the Kingdom of Ingary want to stop the war, but on the other side, the Kingdom of Strangia carries on the war and continues to attack the enemy army.

\item \textit{Friendship}: friendship is a theme recurrent. During Howl's research, Sophie is accompanied by her friend Calcifer. Their friendship is always growing. Throughout the story Sophie creates new friendly relationships with some characters who will help her finding Howl.

\item \textit{Hope and trust}: Sophie is involved in a magical reality unknown to her and the only chance to find her beloved is trusting Suliman and hoping for the legend of the desert djinn  to be true.

\end{itemize}
