\section{Plot}

\subsection*{Prologue}
Sophie has discovered she is a witch and she is learning how to talk with objects, but she is still a beginner.

Suddenly Suliman sends Howl on a mission in order to understand the reasons why the war between Kingsbury and Strangia has not already ceased.

\subsection*{Act 1 (levels 1 and 2)}
Weeks after Howl's departure, Sophie begins getting worried for him because the war is still going on and they haven't heard from him for three weeks.

She goes visiting Suliman and she asks her for some information about Howl and the mission he is carrying on. Suliman tells her that Howl has gone to Dynamia, the capital of Strangia, but she lost communication with him three weeks ago too.

Sophie wants to leave to help Howl, but Suliman discourages her because it is very dangerous. Sophie doesn't care because she cannot stand still while Howl is danger. In order to help Sophie in some way, Suliman gives her a magical ring that can protect her from injuries.

Sophie goes back to the flying castle and tells her friends what she has discovered.

\subsection*{Act 2 (levels 3...6)}
Returned to the flying castle, Sophie puts Calcifer in the magic lantern crafted by Howl and she uses the magic door to reach Dynamia.

While they are roaming through the city they find out that their friend Justin, the prince of Strangia, has been imprisoned by the queen regent because he has come back from Ingary asking to end the war. He has been thought to be secretly a friend of the king of Ingary and so he has been accused of high treason. 

Using their abilities, Sophie and Calcifer enter the castle of Dynamia and they reach the prison. They find the brig where Justin is imprisoned and they free him.

The three of them escape from the fortress and they head to Kingsbury, now under attack by the enemy army. They manage to reach Suliman in the castle, which is still in a safe zone, and Justin explains that the regent is Mizar, a powerful witch who has married his father. Justin's father is dead, so Mizar has become the queen. Suliman knows that Mizar is a djinn because she were the previous court magician of Ingary.

Sophie says that the objects in the castle of Dynamia told her that Howl is imprisoned in the spirits realm. Suliman is not able to send Sophie to the spirits realm, only djinns can, so Suliman tells Sophie about a legendary old djinn who is told to live in the Southern desert.

Hoping the legend is true, Sophie and Calcifer use the castle to fly towards the Southern desert until they find Belzel. They explain to him that one of their friends is trapped inside the spirits realm, so he accepts to help them and he opens a portal.

Sophie and Calcifer enter into the spirits realm, a dimension where everything is crafted by nature and magic. In order to find Howl, they explore many weird areas, fighting against Mizar's demons or solving environmental puzzles. They find Howl, imprisoned and unconscious due to a spell casted by Mizar. They manage to wake him up, they free him and they go back to Earth.

On the way back home Howl tells them his story: he got to Dynamia and almost immediately became aware that a powerful witch had taken the power; he managed to get inside the castle, but once he met Mizar he felt like she was invincible, he got defeated and, finally, Mizar made him fall asleep and imprisoned in the spirits realm.

---------------------

They manage to wake him up and they free him.

Howl briefly explains that he went to Dynamia to find information about a powerful witch who has become the queen. He has been able to defeat her guards and demons, but the witch, Mizar, overcame him because she has hidden somewhere her heart and so she is almost invulnerable. In order to defeat Mizar, they need to find her heart.Howl briefly explains that he went to Dynamia to find information about a powerful witch who has become the queen. He has been able to defeat her guards and demons, but the witch, Mizar, overcame him because she has hidden somewhere her heart and so she is almost invulnerable. In order to defeat Mizar, they need to find her heart.

\subsection*{Act 3 (level 7)}
Once back to the flying castle, Howl uses the black door to see Mizar's past and uncover the hideout of her heart. They see that Mizar is inside the dormant volcano of Kazan island. She has been rejected by the king of Ingary, so she has run away from Kingsbury. She tore out her heart in order not to suffer anymore and, by this way, she has become evil and she has decided to destroy the kingdom of Ingary.

Sophie, Calcifer and Howl get to Kazan island, where Mizar hid her heart. The volcano is now active, nevertheless they are able to overcome the demon guards until they reach the bowels of the volcano. There appears Mizar, so Howl and Calcifer join forces to fight her. In the meantime, Sophie picks up the heart and Mizar becomes suddenly vulnerable. Sophie has now two choices:
\begin{itemize}
\item \textit{Giving the heart to Howl}: Howl destroys it and Mizar dies.
\item \textit{Giving the heart to Mizar}: Mizar's shriveled heart starts to beat again and she realizes what she has done. She feels guilty and scared and she runs away wondering about what she really wants.
\end{itemize} 

The war ends and Sophie, Calcifer and Howl can go back home.

The king of Ingary and prince Justin sign a peace treaty that establish that, in order to prevent future wars, Strangia is annexed to Ingary.
