\section{Story sections}

\begin{enumerate}
\item \textbf{Flying castle} Sophie finds out she is a witch and she is able to talk with objects.
  
\item \textbf{Castle of Kingsbury} Suliman sends Howl on a mission in order to understand the reasons why the war between the two kingdoms has not already ceased.
  
\item \textbf{Flying castle} Sophie keeps training in magic.
  
\item \textbf{Castle of Kingsbury} Sophie is worried because Howl has been missing for weeks and she finds out what is going on.
  \begin{enumerate}
  \item She goes visiting Suliman because Howl was carrying out a mission for her.
    
  \item Suliman explains to her the situation.

  \item Sophie decides to leave to help Howl.

  \item Suliman tries to discourage her, in vain, so she gives her a magical ring to protect her along the way.

  \item Sophie goes back to the flying castle.
  \end{enumerate}

\item \textbf{Castle of Dynamia} Sophie and Calcifer go to Dynamia. They don't find Howl, but they rescue Justin.

  \begin{enumerate}
  \item Sophie puts Calcifer inside the lantern and, using the magical door, reaches Dynamia, the capital of the kingdom of Strangia.
    
  \item They find out that the new queen regent has given orders to imprison Justin.
    
  \item They get to the castle, but there are some guards who are patroling the zone. They have to find another way to get in. Thanks to a Calcifer’s skill they manage to climb the wall and get inside the castle.
    
  \item Once inside, Sophie talks with some objects and learns that Howl has been kept prisoner in the spirits realm and that prince Justin is still in the jail.
    
  \item Using their skills, Sophie and Calcifer find the brig where Justin is imprisoned and they free him.
    
  \begin{enumerate}
    \item They find the brig of Justin.
    
    \item Justin tells them where they can find the key to open the door of the brig.
	    
    \item Sophie and Calcifer find the key and they free Justin.
  \end{enumerate}
    
  \item The three characters escape from the castle and they get back to the flying castle.
    
  \begin{enumerate}
    \item They flee from the dungeon of the castle.
    
    \item They get out of the castle.
    
    \item They run through the streets of Dynamia till they reach the magic door.
  \end{enumerate}
    
  \item Justin tells them that he has to talk with Suliman.
  \end{enumerate}

\item \textbf{Castle of Kingsbury} Justin says that the regent is Mizar. Suliman explains to Sophie how to save Howl.

  \begin{enumerate}
    \item Justin explains to Suliman that the regent is Mizar.
    
    \item Sophie tells Suliman that Howl is imprisoned inside the spirits realm.
    
    \item Suliman is not able to directly send Sophie to the spirits realm, only djinns can. So Suliman tells Sophie where she can find Belzel, a legendary old djinn.
    
    \item Sophie goes back to the flying castle.
  \end{enumerate}

\item \textbf{Southern desert} Sophie and Calcifer reach Belzel's house and he sends them to the spirits realm.

  \begin{enumerate}
  \item Sophie uses the flying castle to get to the desert in the southern region of Ingary.
    
  \item Sophie finds Belzel's house.
    
  \item Sophie explains the situation to Belzel and she convinces him to open a portal towards the spirits realm.
    
  \item Belzel teaches Sophie a new spell to defend herself and her friends from the evil spirits.
    
  \item Belzel creates the portal and Sophie and Calcifer pass through it.
  \end{enumerate}

\item \textbf{Spirits realm} Sophie and Calcifer go to spirits realm and they rescue Howl.

\item \textbf{Flying castle} Sophie, Calcifer and Howl find Mizar's heart hideout.

  \begin{enumerate}
  \item Howl uses the black door to see Mizar's past and understand what is her weak point.
    
  \item They see that Mizar was rejected by the king of Ingary (this is the reason why she wants to continue the war against Ingary) and they also see that she tore out her heart (her weak point) in order not to suffer anymore.
    
  \item They see that Mizar has hidden her heart in a dormant volcano in Kazan island.
  \end{enumerate}
    
\item \textbf{Kazan island} Sophie, Calcifer and Howl face Mizar and defeat her.

  \begin{enumerate}
  \item Sophie, Calcifer and Howl reach Kazan island with the flying castle.
    
  \item They pass through the bowels of the volcano.
    
  \item They overcome traps and enemies.
    
  \item They find Mizar's heart.
    
  \item Howl tries to pick up the heart but doing so a trap is activated and Mizar appears.
    
%  \item While Howl and Calcifer fight with Mizar, Sophie picks up the heart and decides what to do with it.
    
%  \begin{enumerate}
  \item Howl and Calcifer fight against Mizar, in the meantime Sophie picks up the heart and Mizar becomes suddenly vulnerable.
    
  \item Sophie decides whether giving the heart either to Howl or Mizar.
    
    \begin{enumerate}
    \item \textit{Giving the heart to Howl}: Howl destroys it and Mizar dies.
      
    \item \textit{Giving the heart to Mizar}: Mizar regrets what she has done and she accepts to be imprisoned.
    \end{enumerate}
%  \end{enumerate}
    
  \item The war ends and Sophie, Calcifer and Howl go back home.
  \end{enumerate}

\end{enumerate}
