\section{Story}

\textit{In the story writing it has been used the screenplay format to highlight the cutscenes.}\\\\

When Sophie and Calcifer arrive in Dynamia it is late afternoon. They find themselves in a dead end in the suburbs of Dynamia.

\textbf{Calcifer (disgusted)}: What’s this smell!?

They exit from the dead end moving on to a street crossed by a canal. They can hear the noise of the water on their way.

\begin{screenplay}
\extslug[afternoon]{Dynamia}

The camera  moves around Sophie to show streets and canals. 

\begin{dialogue}[amazed]{Sophie}
This city is so beautiful!
\end{dialogue}

The camera rises up to show the city, suggesting the possible paths and, eventually,  zooming on the location of the castle. The camera rotates and returns behind Sophie's shoulders. 

\begin{dialogue}[worried]{Calcifer}
Look how much water! Be careful! Don’t let me fall!
\end{dialogue}
\end{screenplay}
\vspace{1em}

\textbf{Sophie (discouraged)}: Dynamia is so big! Where Howl could be?

\textbf{Calcifer}: I can’t feel his magic. He could be anywhere.

\textbf{Sophie (resolute)}: We need information. We may start to ask someone.

\textbf{Calcifer}: Yes, you're right. Hey, look over there.

On the way, Sophie sees two manifests representing a dark-skinned woman with a crown. She can talk to it.

\textbf{Sophie}: Hello, manifest. Who is this woman?

\textbf{Manifest (solemn)}: She is our enlightened and beloved Queen regent. Long live the Queen!

\textbf{Calcifer}: No, Sophie. Not there, look here! A big market is set up in the big place of Dynamia! We may find information there.

\textbf{Sophie}: Great idea! Let's go!

\textbf{Calcifer}: Do you think that they sell also a little bit of wood?

[An indicator appears in the map.]

Sophie and Calcifer go to the market. There are two guards on their way.

\textbf{Sophie}: Some guards! Better not be noticed.

They move past the guards and they reach the market, which is located in a huge crowded square where they can hear the buzz of the crowd and the shouting of the merchants in the background.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sophie arrives at the stand in the market pointed by the indicator and finds a merchant that sells fabrics and accessories.
Sophie buys a bit of wool to make new hats.

\textbf{Sophie (thinking)}: This will be perfect for my hats!

\textbf{Sophie}: How affairs are going on? Do you have problems due to war?

\textbf{Merchant (resigned)}: Sure, like any other merchant here. What about you? What a lonely girl is doing here?

\textit{Choice}:
\begin{enumerate}
\item \textit{Lie}:
  
  \textbf{Sophie}: I work out of city, it is very hard there too. I hope the war will end soon.
  
  \textbf{Merchant (low level voice)}: Be careful, the guards could hear you. \textbf{(normal level voice)}: The prince Justine was imprisoned for this cause.
  
  \textbf{Sophie (worried)}: Imprisoned? Where? 

  \textbf{Merchant}: Obviously in the castle. Why are you so worried? Are you in league with the prince? Guards!!!!

  Two guards comes to the market but Sophie runs away before they can even get there and sows them easily. 
  
\item \textit{Bribe him}:
  
  \textbf{Sophie (persuasive)}: I'm a foreigner. May you give me some information about a wizard from Ingary who came here few weeks ago? I can pay you.
  
  \textbf{Merchant}: How much?
  
  \begin{enumerate}
  \item Sophie gives 50 coins to the merchant.

    \textbf{Merchant(annoyed)}: It’s not enough. Don’t waste my time!\\

    Sophie goes away disconsolate.
    
    \textbf{Sophie}: I have heard there is another square in front of the castle, maybe we' ll have better luck there.

  \item Sophie gives 100 coins to the merchant.
    
    \textbf{Merchant}: Well I don't know much about any wizard from Ingary. After the prince Justin has been imprisoned ...

    \textbf{Sophie (incredulous)}: Wait, wait, wait! What? Justin has been imprisoned?!
    
    \textbf{Merchant}: Yes, he tried to persuade the queen to end the war and he has been accused of high treason.
    
    \textbf{Sophie}: Really? And where is he now?
    
    \textbf{Merchant}: Obviously, in the prison of the castle. But be careful! The castle is surveilled everywhere by many guards, except for the west wall because they think it is too high for anyone, but, maybe, not for you...
    
    \textbf{Sophie (hasty)}: Okay, okay thank you! I have to go!!
  \end{enumerate}
\end{enumerate}

Sophie heads to the castle.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sophie and Calcifer walk down the main street, but they suddenly see a demon who is looking around.

\begin{screenplay}
\extslug[afternoon]{Dynamia}

Sophie and Calcifer hide behind a corner. The camera focuses on the demon.

\begin{dialogue}[worried]{Sophie}
Oh no, that’s a demon!
\end{dialogue}
\begin{dialogue}[feisty]{Calcifer}
Don’t worry, leave it to me!
\end{dialogue}

The camera focueses on a side street where Sophie looks up at a side street.

\begin{dialogue}{Sophie}
I think we should avoid it.
\end{dialogue}

\begin{dialogue}{Calcifer}
...Or fight it!
\end{dialogue}
\end{screenplay}
\vspace{1em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textit{Choice}
\begin{enumerate}
  \item Sophie and Calcifer fight the demon.
  \item Sophie and Calcifer go through another way.
\end{enumerate}
  
Sophie and Calcifer reach the main square. There are many people and some newsboys.

\textbf{Newsboy}: Breaking news! Prince of Strangia accused of high treason and sentenced to death. Tomorrow morning the public execution!

\textbf{Sophie}: Oh no, we must hurry!

The castle is surrounded by the walls and the gate is patrolled by many guards.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Sophie}: We cannot pass through this way, there are too many guards. Better find another way.

If Sophie tries to go through the gate, the guards will block her.

\textbf{Guards}: Hey, where are you going?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sophie and Calcifer walk along the walls until they find a point where there are some sloping bricks. Nearby there is a pile of old debris.
In a few meters there is a secondary entrance to the castle patrolled by two guards.

\textbf{Calcifer}: Look! An entrance!

\textbf{Sophie}: Wait, we can also use these.

\textit{Choice}
\begin{enumerate}
  \item \textbf{Puzzle}: Calcifer use the debris to create a four-legs construction. He climbs the wall with Sophie thanks to the sloping bricks, then he goes down on the other side without being spotted.\\
  \textbf{Sophie}: Calcifer, you are amazing!\\
\textbf{Calcifer (proud)}: Of course I am!\\
\textbf{Sophie}: Now go back to normal, they will find us in a moment.\\
\textbf{Calcifer (resigned)}: Yeah…
  \item \textbf{Fight}: Sophie and Calcifer defeat the two guards and cross the entrance.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Thanks to the high grass, Sophie and Calcifer cross the courtyard of the castle without being spotted by the guards (now hostile) and the demons.

They reach an open door. They don’t see anyone inside.

\begin{screenplay}
\intslug[afternoon]{Castle of Dynamia, ground floor, old storage}

Sophie, afraid of the darkness, looks around. The camera rotates to show the old storage. On the shelves there are many metal cans and wood boxes. On the ground there are some sacks of grain.

\begin{dialogue}{Sophie}
Hello…?
\end{dialogue}
\begin{dialogue}[cheerful]{Objects}
 Hello!
\end{dialogue}
\begin{dialogue}{Box 1}
 Finally someone has come!
\end{dialogue}
\begin{dialogue}{Can 1}
 Do you want some beans?
\end{dialogue}
\begin{dialogue}{Can 2}
Or some tuna?
\end{dialogue}
\begin{dialogue}[worried]{Sophie}
Ssh! Shut up!
\end{dialogue}
The boxes and the cans stop talking.
\begin{dialogue}{Sophie}
Can you tell me where is the prison?
\end{dialogue}
\begin{dialogue}[surprised]{Can 2}
The prison?
\end{dialogue}
\begin{dialogue}[surprised]{Box 2}
Why the prison?
\end{dialogue}
\begin{dialogue}{Sophie}
Please, I must free a friend of mine.
\end{dialogue}
\begin{dialogue}{Box 1}
Oh, a friend.
\end{dialogue}
\begin{dialogue}{Sack 1}
You can go by that way.
\end{dialogue}
The sack indicates a door on the left.
\begin{dialogue}{Can 2}
But there are a lot of guards!
\end{dialogue}
\begin{dialogue}{Box 1}
You should avoid them!
\end{dialogue}
\begin{dialogue}{Sophie}
Thank you, but... how?
\end{dialogue}
\begin{dialogue}{Sack 1}
You can use the secret passages.
\end{dialogue}
\begin{dialogue}{Box 1}
Look for the old torches. They all hide a secret passage!
\end{dialogue}
\begin{dialogue}{Can 2}
But they want let you pass easily!
\end{dialogue}
\begin{dialogue}{Can 1}
You must solve their puzzles!
\end{dialogue}
\begin{dialogue}[grateful]{Sophie}
Thank you, thank you very much. Oh, would you happen to know something about a powerful magician called Howl?
\end{dialogue}
\begin{dialogue}{Can 2}
Howl?
\end{dialogue}
\begin{dialogue}{Box 1}
Sorry, we don’t know any Howl.
\end{dialogue}
\begin{dialogue}{Can 1}
But we heard about a magician!
\end{dialogue}
\begin{dialogue}{Sack 1}
Some days ago we heard two guards talking about a powerful wizard.
\end{dialogue}
\begin{dialogue}{Box 2}
He has been defeated by the queen regent and he has been imprisoned in the spirits realm.
\end{dialogue}
\begin{dialogue}{Calcifer}
Oh no, I knew he was in danger.
\end{dialogue}
\begin{dialogue}{Sophie}
My poor Howl! I’m so frightened for him. Wait, where do you say he is?
\end{dialogue}
\begin{dialogue}{Box 2}
The spirits realm.
\end{dialogue}
\begin{dialogue}{Box 1}
Or something like that.
\end{dialogue}
\begin{dialogue}{Sophie}
Where is it?
\end{dialogue}
\begin{dialogue}{Can 1}
We don’t know.
\end{dialogue}
\begin{dialogue}{Can 2}
We are just cans!
\end{dialogue}
\begin{dialogue}{Sophie}
Ok, ok. Thank you very much. Now we have to go.
\end{dialogue}
\begin{dialogue}{Sack 1}
Watch out for the queen regent.
\end{dialogue}
\begin{dialogue}{Box 1}
And the guards!
\end{dialogue}
\begin{dialogue}{Can 1}
And the demons!
\end{dialogue}
\end{screenplay}
\vspace{1em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sophie and Calcifer follow the indication of the objects and they reach the guards locker room. There is a door and a small window that allows them to see a guard and a demon. On the wall there is an old and rusty torch.

\textit{Choice}
\begin{enumerate}
  \item \textbf{Puzzle}:\\
    \textbf{Sophie}: Excuse me...\\
    \textbf{Torch (taken by surprise)}: Secret passage? What secret passage?!\\
    \textbf{Sophie}: Ssh. Please, I need to find a friend. \\
    \textbf{Torch (determined)}: No, lady. No favors. If you want to pass, you must solve my puzzle.
    Sophie solves the puzzle and she uses the secret passage to reach the first floor.

  \item \textbf{Fight}: Sophie and Calcifer open the door and defeat the guard and the demon, then they go upstairs.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sophie and Calcifer reach a corridor patrolled by two guards and a demon.

\textit{Choice}
\begin{enumerate}
  \item \textbf{Puzzle}: They hide in the rooms, they wait for the enemies to move on, and then they move on until they reach the end of the corridor. The stairs are locked, so they solve another puzzle and use the secret passage.
  If the enemies come closer, the torch warn Sophie:
  \textbf{Torch (in a very polite way)}: Excuse me, Miss, the guards are approaching.
  Sophie and Calcifer cannot hide in a room because the door is too far, but they can hide in a nearby empty box.

  \item \textbf{Fight}: Sophie and Calcifer defeat the enemies and they take the key to unlock the stairs.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sophie and Calcifer are in front of a room. There are two small windows that allows them to see two guards, two demons and a set of keys. Alongside the door of the room there is another torch. Near the wall there is a box full of glass bottles. The door for the guards courtyard is locked.

\textit{Choice}
\begin{enumerate}
  \item \textbf{Puzzle}: Sophie solves the puzzles and she uses the secret passage with Calcifer. At the end of the passage they can see the enemies walking around, so they cannot enter.\\
  They exit the passage and Sophie throws a glass bottle against the door, then she returns in the secret passage with Calcifer. The guards and the demons, alarmed, exit the room, so Sophie and Calcifer can enter the guards room and take the key.\\
  They wait for the enemies to return in the room and then they unlock the door to the guards courtyard.

  \item \textbf{Fight}: Sophie and Calcifer enter the guards room and defeat the enemies, then they take the key to unlock the door to the guards courtyard.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sophie and Calcifer see the captain of the guards. He is bigger than the other guards and he has a strong and dreadful magic aura.

\textbf{Sophie (at low voice)}: So, what now?

\textbf{Calcifer (at low voice)}: Look! That door! I'm sure Justin is down there.

\textit{Result from previous choices}
\begin{enumerate}
  \item \textbf{Puzzle}:\\
  \textbf{Sophie (at low voice)}: That man is scary. Let's keep quiet and surround them.\\
  \textbf{Calcifer (at low voice)}: I'm mute.\\
  They hide in the high grass and walk around the captain without being spotted until they reach the entrance to the prison.

  \item \textbf{Fight}:\\
  \textbf{Sophie (at low voice)}: Ok, we can handle this.\\
  \textbf{Calcifer (at low voice)}: I'm ready!\\
  They defeat the captain and they reach the entrance to the prison.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sophie and Calcifer go downstairs and they find Justin. He is gaunt and dirty, but he is not injured.

\textbf{Justin (surprised and worried)}: Sophie! Calcifer! Guys, what are you doing here!? It is so dangerous!

\textbf{Sophie}: We are here to help you. They'll be executed tomorrow!

Sophie unlocks the cell and Justin is free.

\textbf{Sophie}: Now let's go, we must hurry.

\textbf{Justin}: Wait, there is another way. You don't know it, but this castle is full of secret passages.

Justin start touching a wall.

\textbf{Justin (continued)}: I'm pretty sure there is one right...

They here a \textit{tac}.

\textbf{Justin (continued)}: ... there.

Sophie, Calcifer and Justin go through the secret passage and they exit in the main courtyard.

\textbf{Justin}: This way. Hurry! 

They exit the castle and reach a docking point where there are some gondolas.

\textbf{Justin}: Let's use a gondola.

\textbf{Calcifer (worried)}: WHAT! You wanna use that scary thing?!

They jump on a gondola.

\textbf{Sophie}: Justin, do you know how to drive it?

Justin picks up an oar.

\textbf{Justin}: Ehm... not really.

Two guards get close to them.

\textbf{Guard 1}: Hey what are you doing?

\textbf{Guard 2}: What? The prince is free! Pull the alarm! The prisoner is running!

\textbf{Calcifer (worried)}: Sophie, use your magic!

\textbf{Sophie (in a hurry)}: Please, move, gondola. We need to go.

\textbf{Boat}: Hello, Sophie. Tell me where you want to go and I will take you there. I’m yours to command.

\textbf{Sophie (in a hurry)}: That way! Go that way!

The gondola starts moving and Sophie guides it through the city, careful to avoid the guards and the demons.

They dock near the dead end where is placed the secret passage for the flying castle. They go there and pass through the door.
