\section{Secondary objectives}
In addition to the main mission, the player can carry on some optional missions that expand some elements of the main story and reveal more details about the world itself.

\subsection{Talk to all the manifests}
In the city there are many manifests. The player can talk to them to discover more details about the current situation of Strangia, in particular of Dynamia.

All the manifests has been made on direct order or Mizar to legitimate her role as regent queen and to encourage the people to fight against Ingary.

\textbf{Reward}: TODO

\subsubsection*{Manifest 1}
The manifest represents Mizar with the crown.

\textbf{Sophie}: Hello, manifest. Who is this woman?

\textbf{Manifest 1 (solemn)}: She is our enlightened and beloved Queen regent. Long live the Queen!

\subsubsection*{Manifest 2}
The manifests represents an evil version of the King of Kingsbury.

\textbf{Sophie}: Hello, manifest. Who is this man?

\textbf{Manifest 2 (disgusted)}: Man? He is not a man! He is the personification of evil! Death to the king of Ingary!

\subsubsection*{Manifest 3}
The manifests represents some soldiers with a flag of Dynamia.

\textbf{Sophie}: Hello, manifest. Who are those men?

\textbf{Manifest 3 (resolute)}: This men are our beloved sons, who fight for our freedom. Ingary will not enslave us! Fight for the country, proud sons of Dynamia!

\subsubsection*{Manifest 4}
The manifests represents a woman holding a baby.

\textbf{Sophie}: Hello, manifest. Who is this woman?

\textbf{Manifest 4 (sad)}: This woman is any woman of Dynamia. Ingary has killed her husband, her child is an orphan, but she won't cry. She has to be strong for the sake of the country. Be strong, women of Dynamia!

\subsubsection*{Manifest 5}
The manifests represents some poor people.

\textbf{Sophie}: Hello, manifest. Who are these people?

\textbf{Manifest 5 (resolute)}: They are the future people of Dynamia if we don't stand and fight against Ingary. Ingary wants to steal our riches, but we won't let them!

\subsubsection*{After talking to all the manifests}
\textbf{Sophie (worried)}: Those manifests are all liars. Ingary wants peace for everyone.

\textbf{Calcifer (resolute)}: Don't worry, Sophie. I'm sure Howl will fix all this in a moment.

\textbf{Sophie}: You are right. Let's hurry and find him!


\subsection{Talk to all the monuments}
In the city there are many monuments. The player can talk to them to discover more details about the history of Strangia, in particular of Dynamia.

Most of the monuments are related to the royal family or some important historical figure, such as the wizard-architect who designed the castle of Dynamia.

\textbf{Reward}: TODO


\subsection{Rebuild the bridge}
Use Calcifer's ability to build a new bridge using some debris found nearby the mission location.

There are many small piles of debris in the ghetto area, the player has to collect five of them to rebuild the bridge.

The player can find the mission by following the indications of some people in the ghetto area who says that a bridge is collapsed.

\textbf{Reward}: TODO (a rare material)

\subsubsection*{Starting mission cutscene}
\begin{screenplay}
\extslug[afternoon]{Dynamia, ghetto area}

A tall man is working on some planks of wood near a collapsed bridge.

\begin{dialogue}{Sophie}
Excuse me, do you need help?
\end{dialogue}

\begin{dialogue}{Tall man}
Oh, you can bet! The bridge is collapsed a week ago and no one knows what to do. I asked to the guards to repair it, but they reply they are too busy. At this time, any help will be grateful.
\end{dialogue}

The tall man goes back to working.

\begin{dialogue}{Sophie}
Calcifer, can you do something?
\end{dialogue}

\begin{dialogue}{Calcifer}
I think so, but I need some debris.
\end{dialogue}

\begin{dialogue}{Sophie}
Ok, let's find some.
\end{dialogue}

\end{screenplay}

\subsubsection*{Ending mission cutscene}
\begin{screenplay}
\extslug[afternoon]{Dynamia, ghetto area}

Calcifer uses the collected debris to build a new bridge.

\begin{dialogue}[excited]{Tall man}
Oh, you are amazing! Thank you! Thank you very much! Here. Take this. You've earned it!
\end{dialogue}

Sophie obtains TODO.

\end{screenplay}



\subsection{Help the traitor guard}
Find and destroy some evidence that may incriminate a traitor guard.

After fulfilling the mission, the guard will give to Sophie a map of the castle.

\textbf{Reward}: TODO


\subsection{Help the dissident councilman}
Help a dissident councilman to reach the port and take a boat to leave Dynamia before the guards get him.

The player can use diversions to trick the guards or he/she can fight them.

\textbf{Reward}: TODO


\subsection{Help the doctor}
Find some seaweed that grows on the wooden stakes of the docking points.

The doctor will tell to Sophie about the disease that killed the king.

\textbf{Reward}: TODO
