\section{Main themes}
% The game story is based on the 'Howl's Moving Castle' film, directed by Hayao Miyazak. It is a sequel of the film and cause of this there are both some themes and recurrent moral of the film, and new themes.

There are some themes and recurrent moral in the game story:
\begin{itemize}
\item \textit{Love}:
  the story of the game is created around two love story that have two different finals.\\
  The first was the love failure of Mizar that has made her the antagonist.
  The second, on the other hand, is the love story of Sophie and Howl. %, which continues from the film.
  Sophie exalts the love theme because she willing do anything to rescued Howl.
  
\item \textit{Vengeance}:
  Vengeance is the reason why the war is going on. Mizar is animated by it because she had a filure in love.
  
\item \textit{Conflict}:
  there is one main conflict in the story, between the Kingdom of Strangia and The Kingdom of Ingary which fights in a recurrent war.
  On one side, the Kingdom of Ingary, would want to stop the war but in the other side, the Kingdom of Strangia, carries on the war and continues to attack the enemy army.
  
\item \textit{Friendship}:
  Friendship is a theme recurrent. Sophie in Howl's research is accompanied by her friend Calcifer.
  Their friendship is always growing. Throughout history Sophie creates new friendly relationships with some characters that will help
  her find Howl.

\item \textit{Hope and trust}:
  Sophie is involved in a magical reality unknown to her and the only chance to find her beloved is trusting Suliman and hoping for the legend of the desert genius.
  
\item \textit{Forgiveness}:
  The game story has to two final. The player can decide to forgive Mizar in the end of the story. This final gives importance to the act of forgiveness.

\end{itemize}
