\section{Plot}

\subsection*{Prologue}
Sophie has discovered she is a witch and she is learning how to talk with objects, but she is still a beginner.

Suddenly Suliman sends Howl on a mission in order to understand the reasons why the war between the two kingdoms has not already ceased.

\subsection*{Act 1}
Weeks after Howl's departure, Sophie begins getting worried for him because the war is still going on and they haven't heard from him for three weeks.

She goes visiting Suliman and ask her for some information about Howl and the mission he is carrying on. Suliman tells her that Howl has gone to Dynamia, the capital of Strangia, but she lost communication with him three weeks ago too.

Sophie wants to leave to help Howl, but Suliman discourages her because it is very dangerous. Sophie doesn't care because she cannot stand still while Howl is danger. In order to help Sophie in some way, Suliman gives her a magical ring.

Sophie goes back to the flying castle and tells her friends what she has discovered.

\subsection*{Act 2}
Sophie puts Calcifer in the magic lantern crafted by Howl and she uses the magic door to reach Dynamia.

While they are roaming through the city they find out that Justin, the prince of Strangia, has been imprisoned by the queen regent because he has come back from Ingary asking to end the war, but he has been thought to be secretly a friend of the king of Ingary and so he has been accused of high treason. They decide to go save him.

Using their abilities, Sophie and Calcifer enter the castle of Dynamia and they reach the prison. They find the brig where Justin is imprisoned and they free him.

The three of them escape from the castle and they get back to the flying castle. They head to the castle of Kingsbury and Justin reveals that the regent is Mizar. Sophie also says to Suliman that the objects in the castle of Dynamia told her that Howl is imprisoned in the spirits realm. Suliman is not able to send Sophie to the spirits realm, only djinns can. So Suliman tells Sophie about a legendary old djinn who is told to live in the southern desert.

Hoping the legend is true, Sophie and Calcifer fly, using the castle, towards the Southern desert until they see an house. Once inside they met the owner, the djinn described in the legend, Belzel, and they explain to him that one of their friends is trapped inside the spirits realm. Belzel is glad to help them and opens a portal for the parallel dimension and teaches Sophie a new spell to defend herself.

\subsection*{Act 3}

Sophie and Calcifer enter into the spirits realm and they begin exploring till they find Howl who is shackled by magical chains. They manage to melt them using Calcifer's fire and so they are free to go back to the Earth.
Once back, Howl uses the black door to see Mizar’s past and understand what is her weak point: They see that Mizar was rejected by the king of Ingary (this is the reason why she wants to continue the war against Ingary) and they also see that she tore out her heart (her weak point) in order not to suffer anymore and she hid it inside the Kazan island dormant volcano.

They get to island and they reach the bowels of the volcano defeating the demon guards who are patrolling the zone. Howl finds the heart and try to pick it up, but doing so a trap is triggered and Mizar appears. Howl and Calcifer begin to fight her and in the meantime Sophie picks up the heart and Mizar becomes suddenly vulnerable.
Sophie has now two choices:
\begin{itemize}
\item \textit{Giving the heart to Howl} : Howl destroys it and Mizar dies.
\item \textit{Giving the heart to Mizar} : Mizar regrets what she has done and she accepts to be imprisoned.
\end{itemize} 
The war ends and Sophie, Calcifer and Howl go back home.