\section{Setting}
The story is set in a far away universe in a unspecified region of the Earth, where humans, magicians and djiins live.
\begin{itemize}
\item \textit{Humans}: the most common ethnic group. They live in contact with magicians. 
\item \textit{Magicians}: they can hold magic powers. They are less common than humans.
\item \textit{Djiins}: this ethnic group is so rare that it is considered like a legend. They can enter in the realm of spirits.
\end{itemize}
Each of these speaks the same language and lives according to the norms of civilized countries.
The atmosphere in the region resembles that of Japan in the early 1900s and it is organized in many different kingdom.
Each king holds a court magician to be helped in the political and military affairs of the kingdom.

Although the region seems safe and quiet the kingdom of Kingsbury is at war with the near Kingdom of Strangia.
The current war is fighted by soldier, humans and wizards, chosen and called of duty from the court magician.
Howl will leave responding to duty but will be victim of a trap. Sophie will go to rescue him crossing the region territories.

In particular:
\begin{itemize}
\item \textit{Wastelands}:
  are the lands in the suburbs of Kingsbury. Inside it there is a Moving Caslte where Howl and Sophie live. The Moving Castle can teleport you in some region place.
\item \textit{Kingdom of Kingsbury}:  
\item \textit{Kingdom of Strangia}: is the first place of the Sophie's journey. 
\item \textit{Southern desert}: this is a big uninhabited part of the region. Nobody lives here except a legendary djiin. No one knows him but between the eldest magician it is common knowing his legend.
\item \textit{Spirit realm}:
\item \textit{UNKNOWN}:
\end{itemize}



