\section{Settings}
The story is set in an alternative version of the Earth, where humans, magicians and djinns live.

%The story is set in an alternative universe, in a unspecified region of the Earth, where humans, magicians and djiins live.

\begin{itemize}
	\item \textit{Humans}: the most common race. They live in contact with magicians.

	\item \textit{Magicians}: humans with magic powers. They are less common than humans.

	\item \textit{Djiins}: this race is so rare that it is considered like a legend. They can enter into the spirits realm.
\end{itemize}

Everybody speaks the same language and lives according to the norms of civilized countries.

The atmosphere in the region resembles that of Japan in the early 1900s and it is organized in many different kingdoms.

Each king holds a court magician who helps him in the political and military affairs.

%Although the region seems safe and quiet, 

The kingdom of Ingary is at war with the near kingdom of Strangia. The war is fighted by soldiers and wizards.

%The current war is fighted by soldiers and wizards, called to duty by the court magicians on behalf of the kings.

\subsection{Locations}
\begin{itemize}
	\item \textit{Moving Castle}: it flies around the skies of Ingary. There is a magic door that lets you teleport in some places.
	\item \textit{Kingsbury}: the capital of the kingdom of Ingary. It is a rich city placed on a river in a wide plain.
	\item \textit{Dynamia}: the capital of the kingdom of Strangia. It is built on a lagoon and its streets are canals.
	\item \textit{Southern desert}: a big uninhabited region. According to a legend, an old powerful djinn lives here.
	\item \textit{Spirits realm}: a magical dimension where there are the spirits of dead people. There are no artificial things, everything is crafted by nature and magic.
	\item \textit{Kazan island}: a volcanic island away from the coasts of the continent where Mizar has hidden her heart.

%	\item \textit{Kazan island}: a volcanic island away from the coasts of the continent. In the depths of the dormant volcano Mizar has hidden her heart.
\end{itemize}
