\section{Story flowchart}

\begin{enumerate}
\item \textbf{Moving castle} Sophie finds out she is a witch and she is able to talk with objects.
  
\item \textbf{Castle of Kingsbury} Suliman sent Howl on a mission in order to understand the reasons why the war between the two reigns has not already ceased.
  
\item \textbf{Moving castle} Sophie keeps training in magic.
  
\item \textbf{Castle of Kingsbury} Sophie is worried because Howl has been missing for weeks and she finds out what is going on.
  \begin{enumerate}
  \item She goes visiting Suliman because Howl was carrying out a mission for her.
    
  \item Suliman explains to her the situation.

  \item Sophie decides to leave to help Howl.

  \item Suliman tries to discourage her, in vain, so she gives her a magical ring to protect her along the way.

  \item Sophie goes back to the moving castle.
  \end{enumerate}

\item \textbf{Castle of Strangia} Sophie and Calcifer go to the kingdom of Strangia. They don’t find Howl, but they rescue Justin.

  \begin{enumerate}
  \item Sophie puts Calcifer inside the lantern and, using the magical door, reaches  the capital of the Kingdom of Strangia.
    
  \item A beggar tells Sophie and Calcifer that a regent has taken the power.
    
  \item They heard from some guards that the new regent has given orders to imprison the prince because Justin has come back from Ingary asking to end the war, but he has been thought to be secretely a friend of the king of Ingary and so he has been accused of high treason.
    
  \item They get to the castle, but there are some guards who are patroling the zone. They have to find another way to get in. Thanks to a Calcifer’s skill they manage to climb the wall and get inside the castle.
    
  \item Once inside, Sophie talks with some items and learns that Howl has been kept prisoner in the reign of spirits and that prince Justin is still in the jail.
    
  \item Using their skills, Sophie and Calcifer find the brig where Justin is imprisoned and they free him.
    
  \item The find the brig of Justin.
    
  \item Justin tells them where they can find the key to open the door of the brig.
    
  \item Sophie and Calcifer find the key and they free Justin.
    
  \item The three characters escape from the castle and they get back to the moving castle.
    
  \item They flee from the dungeon of the castle.
    
  \item They get out of the castle.
    
  \item They run through the streets of Strangia till they reach the magic door.
    
  \item Justin tells them that he has to talk with Suliman.
  \end{enumerate}

\item \textbf{Castle of Kingsbury} Justin says that the regent is Mizar. Suliman explains to Sophie how to save Howl.

  \begin{enumerate}
  \item Justin explains to Suliman that the regent is Mizar.
    
  \item Sophie tells Suliman that Howl is imprisoned inside the reign of spirits.
    
  \item Suliman is not able to directly send Sophie to the reign of spirits, only djinns can. So Suliman tells Sophie where she can find her old djinn friend Belzel.
    
  \item Sophie goes back to the moving castle.
  \end{enumerate}

\item \textbf{Southern desert} Sophie reaches Belzel’s place and he sends them to reign of spirits.

  \begin{enumerate}
  \item Sophie uses the moving castle to get to the desert in the south of the kingdom of Ingary.
    
  \item Sophie finds Belzel’s house.
    
  \item Sophie explains the situation to Belzel and she convinces him to open a portal towards the reign of spirits.
    
  \item Belzel teaches Sophie a new spell to defend herself and her friends from the evil spirits.
    
  \item Belzel creates the portal and Sophie and Calcifer pass through it.
  \end{enumerate}

\item \textbf{Reign of spirits} Sophie and Calcifer go to reign of spirits and they rescue Howl.

\item \textbf{Moving castle and e spirit realm}  Sophie, Calcifer and Howl find Mizar’s heart and they defeat her.

  \begin{enumerate}
  \item Howl uses the black door to see Mizar’s past and understand what is her weak point.
    
  \item They see tha Mizar was rejected by the king of Ingary (this is the reason why she wants to continue the war till Ingary will be completely completely deleted) and they also see that she tore out her heart (her weak point) in order not to suffer anymore.
    
  \item They find where Mizar has hidden her heart.
    
  \item Sophie, Calcifer and Howl go towards the place where the heart is hidden but Mizar appears.
    
  \item They pass through the dungeon.
    
  \item They overcome traps and enemies.
    
  \item They find the heart.
    
  \item Howl tries to pick up the heart but doing so a trap is activated and Mizar appears.
    
  \item While Howl and Calcifer fight with Mizar, Sophie picks up the heart and decides what to do with it.
    
  \item Howl and Calcifer fight with Mizar.
    
  \item Sophie picks up the heart and Milzar becomes suddenly vulnerable.
    
  \item Sophie decides whether giving the heart  either to Howl or Mizar.
    
    \begin{enumerate}
    \item \textit{Giving the heart to Howl}: Howl destroys it and Mizar dies.
      
    \item \textit{Giving the heart to Mizar}: Mizar regrets what she has done and accepts to be imprisoned.
    \end{enumerate}
    
  \item Justin becomes the new king. Sophie, Calcifer and Howl go back home.
  \end{enumerate}

\end{enumerate}
