\section{Rewards and collectables}
One of the main components of Sophie's Flying Castle game is finding collectibles throughout the world.
Collectibles are items that are required to be collected in order to achieve 100\%
completion of the game, but they are not compulsorily required to go on in the main storyline. Collectibles, along with coins and crafting materials, are the fundamental part of the reward system of the game; in fact they constitute the prizes for any successful in-game action of the player. Moreover they even grant rewards to all the players who will deeply explore the maps, reaching high percentages of completion of the game.\\

There are three category of collectibles:
\begin{enumerate}
\item \textbf{Hats}: these objects can be hats, wigs and helmets. If they are worn they provide skill bonuses during the game wherever Sophie is, as long as she keeps them on.
\item \textbf{Lanterns}: these objects work as weapons for Sophie. They contain Calcifer and they are evolutions of the basic lantern, given to Sophie at the beginning of the story. While they are held by Sophie, they provide skill bonuses during the combat against enemies. 
\item \textbf{Clothes}: these objects are special clothes that Sophie may get during the game and they provide effects depending on where Sophie is.  
  \end{enumerate}

A player can only use one object per category at a time.

Example: if Sophie had unlocked two or more magic hats, she could still wear only one. But if she had unlocked also a magic lantern, she might wear a hat and hold the lantern.

Collectables can be sold for Difficulty * 10 coins at merchants' stands as well as crafting materials can be sold for half of their buying price at merchants' stands. Collectables can be bought back at the same stand where the player sold them for Difficulty * 20 in case they have been crafted or for the original selling price in case they have been bought (e.g. in case the player sold them by mistake).



\subsection{Level completion rewards}
These collectables are items that Sophie may obtain only by completing specific actions during the course of the main story and they can not be crafted or obtained in an other way.

%These are tied to a small reward in coins, materials or experience and bound to levels of Sophie's abilities.

%The player will receive these items just by playing the main story of the game.\\\\
%There are three category of rewards:
%\begin{enumerate}
%\item \textbf{Hats}\\
  \input{RewardsAndCollectables/tableHatsLevels}
%\item \textbf{Lanterns}\\
  \input{RewardsAndCollectables/tableLanternsLevels}
%\item \textbf{Clothes}\\
  \input{RewardsAndCollectables/tableClothesLevels}
%\end{enumerate}


\subsection{Others collectables and trophies}
These collectables are not related to the main story and the player could get them at anytime during the game. In order to receive them the player has to play the game deeply, exploring areas outside the ones he encountered during the main story flow, investing more time to get higher rewards.
%\begin{enumerate}
%\item \textbf{Hats}\\
  \input{RewardsAndCollectables/tableHats}
%\item \textbf{Lanterns}\\
  \input{RewardsAndCollectables/tableLanterns}
%\item \textbf{Clothes}\\
  \input{RewardsAndCollectables/tableClothes}
%\end{enumerate}


