\section{Howl}

\textbf{Name}: Howl Jenkins Pendragon \\
\textbf{Function}: Victim who has to be rescued first, helper during the final fight then

\subsection{Internal World}

\textbf{Age \& Gender}: 27-30, Male \\
\textbf{Values \& Virtues}: Beauty \\
\textbf{Personality}: Friendly, passionate, emotive, lazy, leader \\
\textbf{Interests}: Magic, body care \\
\textbf{Ethnic Group}: Wizard, Human

\subsection{External World}
\textbf{Environment}: Wastelands, Howl’s Moving Castle \\
\textbf{Education}: High-education \\
\textbf{Social \& Cultural Background}: He has always been famous as one of the most powerful wizards of Ingary \\
\textbf{Look \& Feel}: Young handsome man   \\
\textbf{Job \& Experience}: Experienced wizard \\
\\
\textbf{Relatives \& Relation}:
\begin{enumerate}
\item \textbf{Sophie}: He is in love with her, his partner. He lives with her in the Moving Castle
        with Calcifer
\item \textbf{Calcifer}: He is a long-time friend of him and live with him in the Moving Castle
\item \textbf{Justin}: They barely know each other
\item \textbf{Suliman}:He has a great respect for Suliman, his magic teacher
             He is slightly submissive to her and really takes into consideration what she says
\item \textbf{Mizar}: He hates her because she wants the war to go on and because she trapped him into an inescapable prison 
\item \textbf{Belzel}: No one knows each other
\end{enumerate}

\subsection{Description}
Howl is a powerful Wizard that works as an emissary for the Kingdom of Ingary. In the story he has to be rescued from the Mizar’s trap. He know every secret of the Moving Castle and he is the only one who can transform and edit it.

\subsection{Background story}
Howl is always being notorious as a powerful wizard of Ingary. After that the pact with Calcifer has been broken, he decided to introduce and train Sophie in magic. He created a magic needle that she can use to sew magic hats. Before leaving for the mission he also created a magic lantern for Calcifer. Calcifer, free from the pact, can go out the castle inside the lantern without the Moving Castle being destroyed. Suliman gave him the mission to stop the war, but he disappeared.



